Indexes measures for oak decline severity using phenotypic descriptors

### 2019-08-28 manuscript/manuscript.Rmd
moved figures into own file. Moved adjustment figure to supplementary file. Adjusted and finished site differences figure

***Agrilus* exit hole density (m<sup>-2</sup>)** - density of observed *Agrilus* exit holes across the surveyed trunk area.
$$e = \frac{h}{\frac{2d}{100}\pi}$$
$h$ = number of *Agrilus* exit holes, $d$ = diameter at breast height (cm)
```{r site_differences}
source('../code/site_differences.R')
site_differences %>%
  wrap_plots()
```
```{r descriptor_adjustment,fig.cap='Error bars show ±1SE of the mean.\nDashed red line shows the overall mean.'}
source('../code/descriptor_adjustment.R')
descriptor_adjustment %>%
  wrap_plots()
```
```{r DIspace}
DIspace()
```
```{r}
source('../code/descriptor_contributions.R')
descriptor_contributions %>%
  wrap_plots() + 
  plot_annotation(title = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures',caption = 'Gini importance scores averaged across 100 repetitions')
```
# Discussion
# Conclusions
# References

>>>>

***Agrilus* exit hole density (m<sup>-2</sup>)** - density of observed *Agrilus* exit holes across the surveyed trunk area.
$$e = \frac{h}{\frac{2d}{100}\pi}$$
$h$ = number of *Agrilus* exit holes, $d$ = diameter at breast height (cm)

# Discussion

# Conclusions

# References

# Figures

```{r site_differences,fig.cap='Site differences',fig.height=6}
source('../code/site_differences.R')
grid.arrange(site_differences$a,site_differences$b,nrow = 1)
```

```{r descriptor_adjustment,fig.cap='Error bars show ±1SE of the mean.\nDashed red line shows the overall mean.'}
source('../code/descriptor_adjustment.R')
descriptor_adjustment %>%
  wrap_plots()
```

```{r DI_space,fig.cap=''}
DIspace()
```

```{r descriptor_contributions, fig.cap = ''}
source('../code/descriptor_contributions.R')
descriptor_contributions %>%
  wrap_plots() + 
  plot_annotation(title = 'Descriptor importance scores from random forest models for relative contributions to\ndecline index measures',caption = 'Gini importance scores averaged across 100 repetitions')
```
